troubleshooting

### 2024-09-27 README.Rmd
added support for proteome discoverer exports.

#### Proteome Discoverer

Analysis using a .csv file exported from [proteome
discoverer](https://www.thermofisher.com/us/en/home/industrial/mass-spectrometry/liquid-chromatography-mass-spectrometry-lc-ms/lc-ms-software/multi-omics-data-analysis/proteome-discoverer-software.html)
is supported.

To generate this .csv file:

```{r}
```

@@

fragpipe_prepared_data
```

>>>>

@@

fragpipe_prepared_data
```
#### Proteome Discoverer

Analysis of a PeptideGroups.txt file exported from [proteome
discoverer](https://www.thermofisher.com/us/en/home/industrial/mass-spectrometry/liquid-chromatography-mass-spectrometry-lc-ms/lc-ms-software/multi-omics-data-analysis/proteome-discoverer-software.html) is supported.

To generate this .txt file:
1. Ensure that non-normalized/ non-scaled abundances are included in your 
PeptideGroup table.   
2. File > export > To Text (tab delimited) > Items to be exported - check 
the Peptide Groups box > Export.

Note that the fileIDs of each sample in proteome discoverer (By default 
F1 - Fn) must match the quantCols in colData.

```{r}
peptide_groups_filepath <- system.file(
  "extdata/proteome_discoverer_PeptideGroups.txt",
  package = "mspms"
)

colData_filepath <- system.file("extdata/proteome_discover_colData.csv",
                                package = "mspms")

prepared_pd_data = prepare_pd(peptide_groups_filepath,colData_filepath)

prepared_pd_data
```
